\bf A hierarchical failure-time model for observational data exhibiting infant-mortality and wearout failure modes

### 2017-10-06 paper/paper.tex

\begin{figure}
\centering
\includegraphics[height=.8\textheight]{dm43-shrinkage.png}
\caption{\footnotesize Top: Event plot for all units of Drive-model 43. Data for all units are left-truncated, being observed conditional on survival beyond 12,000 hours.\hspace{\textwidth}Bottom: The dashed step function correponds to the adjusted Kaplan-Meier estimate. Due to the heavy left-truncation, the posterior median (dashed line) follows the ``global model" (dotted line), defined by the GLFP parameters corresponding to the means of the hierarchical distribution, until approximately the first left-truncation time.}
\label{fig:ex-mod-43}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[height=.8\textheight]{dm43-shrinkage.png}
\caption{\footnotesize Top: Event plot for all units of Drive-model 43. Data for all units are left-truncated, being observed conditional on survival beyond 12,000 hours.\hspace{\textwidth}Bottom: The dashed step function correponds to the adjusted Kaplan-Meier estimate. Due to the heavy left-truncation, the posterior median for Drive-model 43 (dashed line) coincides with the posterior median of the ``global model" (dotted line) until the first left-truncation time.}
\label{fig:ex-mod-43}
\end{figure}
